### 2021-07-13 tex/kits.tex
[ writing ] finish kits section

\begin{itemize}
  \item A substitution gives us terms, rather than variables.
        This means that when we use the substitution on a variable, we already
        have a term, and don't need to do any embedding into terms.
  \item When dealing with newly bound variables in \AgdaFunction{bindSub}, we
        need to produce terms, so we embed the newly bound variables into terms
        using \AgdaInductiveConstructor{var}.
  \item We use \AgdaFunction{$\swarrow^t$} instead of
        \AgdaFunction{$\swarrow^v$}, because we are dealing with terms rather
        than variables.
\end{itemize}

@@

To abstract over the similarities between renaming and substitution, we can use
\emph{kits} as introduced by McBride~\cite{McBride05,BHKM12}.

>>>>

\begin{itemize}
  \item A substitution gives us terms, rather than variables.
        This means that when we use the substitution on a variable, we already
        have a term, and don't need to do any embedding into terms.
  \item When dealing with newly bound variables in \AgdaFunction{bindSub}, we
        need to produce terms, so we embed the newly bound variables into terms
        using \AgdaInductiveConstructor{var}.
  \item We use \AgdaFunction{$↙ᵗ$} instead of \AgdaFunction{$↙ᵛ$}, because we
        are dealing with terms rather than variables.
\end{itemize}

@@

To abstract over the similarities between renaming and substitution, we can use
\emph{kits} as introduced by McBride~\cite{McBride05,BHKM12}.
Each of the three differences above is turned into a parameter of
\AgdaFunction{trav} (generalising \AgdaFunction{ren} and \AgdaFunction{sub})
and \AgdaFunction{bindEnv} (generalising \AgdaFunction{bindRen} and
\AgdaFunction{bindSub}).
In the types, \AgdaFunction{Ren} and \AgdaFunction{Sub} are generalised by
\AgdaFunction{Env}\AgdaSpace{}\AgdaBound{K} --- a function from variables in
\AgdaBound{$\Delta$} to \AgdaBound{K}-things in \AgdaBound{$\Gamma$}.

\Env{}

The function \AgdaFunction{trav} produces a term-to-term mapping based on an
environment \AgdaBound{$\rho$}.
Like renaming and substitution, the traversal \AgdaFunction{trav} replaces
variables according to \AgdaBound{$\rho$}, while keeping the rest of the
syntactic forms intact.
The three differences between renaming and substitution present themselves as
requirements of the notion of \emph{kit} we can choose:

\begin{itemize}
  \item In the \AgdaInductiveConstructor{var} case of \AgdaFunction{trav}, we
        apply the environment \AgdaBound{$\rho$} to get a \AgdaBound{K}-thing,
        and need something to turn this \AgdaBound{K}-thing into a term.
        We let \AgdaField{tm} be this context- and type-preserving map from
        \AgdaBound{K}-things to terms.
  \item When dealing with newly bound variables in \AgdaFunction{bindEnv}, we
        need to convert the new variable into a \AgdaBound{K}-thing in order to
        put it into the environment.
        We let \AgdaField{vr} be this context- and type-preserving map from
        variables to \AgdaBound{K}-things.
  \item When working out where to map old variables in an extended context, we
        need \AgdaBound{K}-things to be stable under context extensions.
        We let \AgdaField{↙ᵏ} be the function embedding a \AgdaBound{K}-thing
        into an extended context.
\end{itemize}

\trav{}

The three parameters can be given to these functions by filling the fields of
the \AgdaRecord{Kit} record.

\Kit{}

We may now redefine the types \AgdaFunction{Ren} and \AgdaFunction{Sub} via
\AgdaFunction{Env}, and derive the actions of renaming and substitution from
\AgdaFunction{trav}.
Notice that \AgdaFunction{↙ᵗ} (written out as
\AgdaFunction{ren}\AgdaSpace{}\AgdaFunction{↙ᵛ}) still relies on renaming, but
because \AgdaFunction{ren} is only being used to fill a parameter of
\AgdaFunction{trav}, \AgdaFunction{trav} itself can be used to define
\AgdaFunction{ren} in a non-circular way.
Thus, we have succeeded in avoiding the duplication of code between
\AgdaFunction{ren} and \AgdaFunction{sub}.
%\todo{Distribute code horizontally}

\begin{multicols}{3}
  \noindent\RenSub{} \columnbreak

  \noindent\renKit{} \columnbreak

  \noindent\subKit{}
\end{multicols}

%\noindent
%\begin{tabular}{l|l|l}
%  \begin{minipage}{.25\textwidth}
%    \RenSub{}
%  \end{minipage}
%  &
%  \begin{minipage}{.25\textwidth}
%    \renKit{}
%  \end{minipage}
%  &
%  \begin{minipage}{.25\textwidth}
%    \subKit{}
%  \end{minipage}
%\end{tabular}
